paper

### 2024-09-24 inst/extdata/paperdata/paper.qmd
.

```{r}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
#data("Columbia.RealCase")
print(Columbia.RealCase)

# Set metadata and formula for LimROTS analysis
meta.info <- c("groups" , "Age" , "gender" , "LRRK2.status" , "GBA.status")
B <- 1000  # Number of bootstrap samples
K <- dim(Columbia.RealCase)[1]/2  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "groups"
formula.str <- "~ 0 + groups + Age + gender + LRRK2.status + GBA.status"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

@@

```{r}
plot(limrots.result$q_values)
hist(limrots.result$q_values)
summary(limrots.result$q_values)
```

@@

# Create a volcano plot
ggplot(limrots.result.df, aes(x = limrots.result$corrected.logfc, y = -log10(limrots.result$pvalue) )) +
  geom_point(alpha = 0.8) +
  theme_bw() +
  labs(title = "Volcano Plot", x = "Log Fold Change", y = "-Log10 q.value", color = "True Positive") +
  scale_color_manual(values = c("grey", "red"))+
  geom_hline(yintercept=-log10(0.05), linetype="dashed", color = "blue")+
  geom_hline(yintercept=-log10(0.01), linetype="dashed", color = "black")
```

@@

@@

>>>>

```{r}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
data("Columbia.RealCase")
print(Columbia.RealCase)

set.seed(1234, kind = "default")

data.assay <- assay(Columbia.RealCase)
data.assay <- preprocessCore::normalize.quantiles(as.matrix(data.assay))

# Set metadata and formula for LimROTS analysis
meta.info <- c("groups" , "Age" , "gender" , "LRRK2.status" , "GBA.status")
B <- 1000  # Number of bootstrap samples
K <- dim(Columbia.RealCase)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 10  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "groups"
formula.str <- "~ 0 + groups + Age + gender + LRRK2.status + GBA.status"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

@@

```{r}
plot(limrots.result$q_values)
hist(limrots.result$q_values)
hist(limrots.result$q_values$qvalues)

summary(limrots.result$q_values)
```

@@

# Create a volcano plot
ggplot(limrots.result.df, aes(x = limrots.result$corrected.logfc, y = -log10(limrots.result$q_values$qvalues) )) +
  geom_point(alpha = 0.8) +
  theme_bw() +
  labs(title = "Volcano Plot", x = "Log Fold Change", y = "-Log10 q.value", color = "True Positive") +
  scale_color_manual(values = c("grey", "red"))+
  geom_hline(yintercept=-log10(0.05), linetype="dashed", color = "blue")+
  geom_hline(yintercept=-log10(0.01), linetype="dashed", color = "black") 
```

@@

volcanoplot(fit.ebayes)
plotMD(fit.ebayes)

@@

```{r}
library(ROTS)

rots <- ROTS(data, groups = as.numeric(meta.info$groups), B = 1000, progress = TRUE,
             K = 600, a1= 5, a2 = 1)
```

```{r}
rots.df <- data.frame(p = rots$pvalue, f = rots$logfc)

ggplot(rots.df, aes(x = f, y = -log10(p))) +
  geom_point(alpha = 0.8) +
  theme_bw() +
  labs(title = "Volcano Plot", x = "Log Fold Change", y = "-Log10 q.value", color = "True Positive") +
  scale_color_manual(values = c("grey", "red"))+
  geom_hline(yintercept=-log10(0.05), linetype="dashed", color = "blue")+
  geom_hline(yintercept=-log10(0.01), linetype="dashed", color = "black")
```
